### 2013-10-31 inst/examples/policycosts/writeup.Rmd
exploring table relative costs

```{r graphing-options, include=FALSE}
#opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(dev.args=list(bg="transparent"),
               tidy=FALSE, comment=NA, message=FALSE, warning=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = 
                          element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor = 
                          element_line(colour = "transparent"))
theme_set(theme_notebook)
```

@@

``` {r simulate_policy, dependson=c("policynames", "apples")}
quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"]) 
sims <- list(
  L1 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed), 
  L2 = simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed),
  fixed = simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed),
  increase = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_increase_policy, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_increase(apples["increase"]), seed=seed),
  decrease = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            free_decrease_policy, z_g, z_m, z_i, 
                            opt$D, profit=profit, penalty= free_decrease(apples["decrease"]), seed=seed),
  quad = simulate_optim(f, pars, x_grid, h_grid, x0, 
                            quad_policy, z_g, z_m, z_i, 
                            opt$D, profit=quad_profit, penalty= none, seed=seed)
)
````

``` {r tidy, dependson="simulate_policy"}
#Make data tidy (melt), fast (data.tables), and nicely labeled.
dat <- melt(sims, id=names(sims[[1]]))  
dt <- data.table(dat)
setnames(dt, "L1", "penalty_fn") # names are nice
````

>>>>

```{r graphing-options, include=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
opts_chunk$set(dev.args=list(bg="transparent"),
               tidy=FALSE, comment=NA, message=FALSE, warning=FALSE)
theme_notebook <- theme_grey() + 
                  theme(plot.background = 
                          element_rect(fill = "transparent",colour = NA),
                        panel.grid.minor = 
                          element_line(colour = "transparent"))
theme_set(theme_notebook)
```

@@

``` {r simulate_policy, dependson=c("policynames", "apples")}
quad_profit <- profit_harvest(price = price, c0 = c0, c1 = apples["quad"])

reps <- 1:10
names(reps) = paste("rep", 1:10, sep="_")
sims <- list(
  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L1(apples["L1"]), seed=seed)), 
  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=L2(apples["L2"]), seed=seed)),
  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=fixed(apples["fixed"]), seed=seed))

)
````

``` {r tidy, dependson="simulate_policy"}
#Make data tidy (melt), fast (data.tables), and nicely labeled.
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, "L2", "replicate") # names are nice
setnames(dt, "L1", "penalty_fn") # names are nice
````

```{r }
sims_free <- list(
  L1 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L1_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=none, seed=seed)), 
  L2 = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                      L2_policy, z_g, z_m, z_i, 
                      opt$D, profit=profit, penalty=none, seed=seed)),
  fixed = lapply(reps, function(x) simulate_optim(f, pars, x_grid, h_grid, x0, 
                         fixed_policy, z_g, z_m, z_i, 
                         opt$D, profit=profit, penalty=none, seed=seed))
)
````

``` {r }
#Make data tidy (melt), fast (data.tables), and nicely labeled.
free <- melt(sims_free, id=names(sims_free[[1]][[1]]))  
dt_free <- data.table(free)
setnames(dt_free, "L2", "replicate") # names are nice
setnames(dt_free, "L1", "penalty_fn") # names are nice
````

```{r}

# Profit when accounting for penalty when present
optimal_cost <- dt[, sum(profit_fishing), by=penalty_fn ] 
# Profit when ignoring penalty when present
ignore_when_present <- dt[, sum(profit_fishing_alt), by=penalty_fn] 
# Profit when assuming penalty when it is absent
assume_when_absent <- dt_free[, sum(profit_fishing), by=penalty_fn]
# Profit when ignoring penalty when it is absent
optimal_free <- dt_free[, sum(profit_fishing_alt), by=penalty_fn]

# Normalize by the optimal 
ignore_when_present$V1 <- ignore_when_present$V1/optimal_cost$V1
assume_when_absent$V1 <- assume_when_absent$V1/optimal_free$V1

# Name and merge columns
setnames(ignore_when_present, "V1", "ignore_cost")
setnames(assume_when_absent, "V1", "assume_cost")
error_costs = merge(ignore_when_present, assume_when_absent, "penalty_fn")

error_costs

### additional plots based on simulations under the correct model
